### 2022-04-08 manuscript.tex
tubafigurefix [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/bd0e4c0d29a553d0a2e15f89b42a89cd700418db.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/bd0e4c0d29a553d0a2e15f89b42a89cd700418db/checks
https://github.com/scherzerthesis/thesis/actions/runs/2115380968

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/da43cb74d176c31bc2ce988d80e925e8ab7b75fa/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/da43cb74d176c31bc2ce988d80e925e8ab7b75fa}{scherzerthesis/thesis@da43cb7}
on April 7, 2022.

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/bd0e4c0d29a553d0a2e15f89b42a89cd700418db/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/bd0e4c0d29a553d0a2e15f89b42a89cd700418db}{scherzerthesis/thesis@bd0e4c0}
on April 8, 2022.
